Universal Anonymous Signatures

### 2022-06-03 prism-backend/research/gsac/model-uas.tex
Upgrading definitions and proofs.

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of credentials \scred,
  each with a matching issuer key in \sipk.
  The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval,\ceval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation
  function \feval, returns signature \sig, a plaintext value \yeval,
  and an encrypted value \ceval. For readability, we use \Sig to denote
  the tuple $(\sig,\yeval,\ceval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval,\ceval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\sig,\yeval,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys in \sipk. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval,\ceval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\CRED[\scid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\Sig = (\sig,\yeval,\ceval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
    \feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
    = 0~\lor \\
    \pcind \yinsp \neq \finsp^\gid(\yeval,\yeval^1,\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
Informally, anonymity must capture two requirements: (1) interactive credential
issuance protocols do not leak any information about the user requesting them;
and (2), signatures do not leak any information about the signer.

\todo{XXX}
We follow a simulation-based approach to define anonymity in \UAS.

simulation-based, definition of the
anonymity property. In the simulation-based approach, we require the adversary
to guess the bit $b$ defining whether it is interacting with the real world,
where it gets signatures by real users, or with a simulation, where all
signatures are simulated and do not contain information about the signer.
This alternative formulation is given in \figref{fig:exp-uas-simanon}, where
$\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,\lbrace\II,\OO\rbrace\GEN,\lbrace\II,
\OO\rbrace\CORR,\WREG)$.

@@

  \centering
  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
    \pcif b = 0: \\
    \parm \gets \Setup(1^\secpar) \\    
    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
    \pcelse: \\
    \parm \gets \SIMSETUP(1^\secpar) \\
    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
    \pcreturn b^*
  }

  \caption{Simulation-based anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-simanon}
\end{figure}

\begin{definition}{(Simulatable Anonymity of \UAS)}
  \label{def:sim-anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\sig,\yeval,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\sig,\yeval,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
      \msg,\feval) \\
      (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0: \pcreturn 1 \\
      \pcif \finsp(\yeval^0,\yeval^1,,\usk,\scred,\msg) \neq \yinsp
      \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\oid,\siid,\Sig,\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
%    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
%    \pcreturn 0 \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
    \pcif \exists \uid \in \HU~\st~\UK[\uid] = \usk~\land \\
    \pcind (\nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]
    \lor \yinsp \neq \yinsp'): \pcreturn 1 \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

>>>>

\begin{description}
\item[$\Setup(\secpar) \rightarrow \parm$.] Given a security parameter \secpar,
  returns a global system parameter variable \parm. We assume that \parm are
  available to all the other functions, even if not explicitly listed in their
  input parameters.
\item[$\IKeyGen(\parm,\fissue) \rightarrow (\ipk,\isk)$.] Given global system
  parameters \parm, and the function \fissue to be used to check that credential
  requestors meet the conditions to be issued a credential, an issuer runs
  \IKeyGen to generate its issuing key pair. 
\item[$\OKeyGen(\parm,\finsp) \rightarrow (\opk,\osk)$.] Given global system
  parameters \parm, and function \finsp, an opener runs \OKeyGen to generate
  its opening key pair. The function \finsp defines the type of utility that
  will be extractable from signatures.
\item[$\UKeyGen(\parm) \rightarrow \usk$.] Given global system parameters
  \parm, returns a user's secret key.
\item[$\langle
  \Obtain(\usk,\ipk,\scred,\attrs),
  \Issue(\isk,\sipk,\attrs))
  \rangle \rightarrow \langle \cred/\bot,\utrans/\bot \rangle$.] %
  This interactive protocol lets a user with key \usk running the
  \Obtain process, receive a credential \cred from an issuer in the system, on
  attribute set $\attrs$. The user leverages a set of credentials \scred,
  each with a matching issuer key in \sipk.
  The user outputs the produced credential \cred, while
  the issuer outputs the protocol transcript \utrans for the produced
  credential.
\item[$\Sign(\usk,\opk,\scred,\msg,\feval) \rightarrow (\sig,\yeval,\ceval)$.] %
  Upon receiving a user secret key \usk, opener public key \opk, a set of
  credentials \scred, a message \msg and evaluation
  function \feval, returns signature \sig, a plaintext value \yeval,
  and an encrypted value \ceval. For readability, we use \Sig to denote
  the tuple $(\sig,\yeval,\ceval)$.
\item[$\Verify(\opk, \sipk,\Sig,\msg,\feval) \rightarrow 1/0$.]
  Checks whether $\Sig = (\sig,\yeval,\ceval)$ is a valid signature
  over message \msg, from a user with credentials issued by issuers with public
  keys in \sipk, for evaluation function \feval and opener key \opk.
\item[$\Open(\osk,\sipk,\sig,\yeval,\msg,\feval) \rightarrow
  (\yinsp,\iproof)/\bot$.]
  Executed by the opener with private key \osk. Receives a signature $(\sig,
  \yeval)$ over message \msg and evaluation function \feval, generated using
  credentials issued by the issuers with public keys in \sipk. If \sig is valid,
  the function outputs a value $\yinsp$.
\item[$\Judge(\opk,\sipk,\yinsp,\iproof,\Sig,\msg,\feval) \rightarrow 1/0$.] %
  Checks if \iproof is a valid opening correctness proof for the value \yinsp,
  obtained by applying \Open to the the signature $\Sig = (\sig,\yeval,\ceval)$
  over message \msg, and for evaluation function \feval. 
\end{description}

@@

        \procedure{$\OBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          %\pcif \exists \cid' \in \scid~\st~\CRED[\cid'] = \bot: \pcreturn \bot \\
          \langle \cred, \cdot \rangle \gets
          \langle \Obtain(\UK[\uid],\PUBIK[\iid],\CRED[\scid],\attrs),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\
        }

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpCorrect(1^\secpar)$}{%
    \parm \gets \Setup(1^\secpar) \\
    (\uid,\oid,\scid,\msg,\feval)
    \gets \adv^{\IGEN,\OGEN,\HUGEN,\OBTISS,\RREG}(\parm) \\
    \pcif \feval \notin \famfeval: \pcreturn 0 \\
    \pcif \OWNR[\scid] \neq \uid: \pcreturn 0 \\
    (\Sig = (\sig,\yeval,\ceval)) \gets \Sign(\UK[\uid],\PUBOK[\oid],\scid,\msg,
    \feval) \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\scid],\Sig,\msg,\feval) = 0: \pcreturn 1 \\
    \pcfor \cid \in \scid \pcdo: \\
    \pcind \textrm{Let}~\scred^{\cid}~\textrm{be the credentials used to obtain}
    ~\cid;~\textrm{Parse}~\PUBIK[\ISR[\cid]]~\textrm{as}~((\cdot,\fissue^{\cid}),\cdot)\\
    \pcind \pcif \fissue^{\cid}(\UK[\uid],\scred^{\cid},\ATTR[\cid]) = 0: \pcreturn 1 \\
    (\yeval^0,\yeval^1) \gets \feval(\UK[\uid],\CRED[\scid],\msg) \\
    \pcif \yeval^0 \neq \yeval: \pcreturn 1 \\
    (\yinsp,\iproof) \gets \Open(\PRVOK[\gid],\PUBIK[\scid],\Sig,\msg,\feval) \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\scid],\yinsp,\iproof,\Sig,\msg,\feval)
    = 0~\lor \\
    \pcind \yinsp \neq \finsp^\gid((\yeval,\yeval^1),\UK[\uid],\CRED[\scid],\msg)): \\
    \pcind \pcreturn 1 \\
    \pcreturn 0
  }  
  \caption{Correctness experiment for \UAS schemes.}
  \label{fig:exp-uas-corr}
\end{figure}

@@

\paragraph{Anonymity.} %
Informally, anonymity must capture two requirements: (1) interactive credential
issuance protocols do not leak any information about the user requesting them;
and (2) signatures do not leak any information about the signer. In both cases,
any leakage must be limited to whatever the user decides to reveal, for
instance, through arbitrary predicates on the attributes of the credentials used
for issuance and signing. We follow a simulation-based approach to capture this.
Basically, the adversary is challenged to distinguish between real and ideal
executions. In both worlds, the adversary can generate and corrupt honest users,
issuers, and openers. Then, in the real world, the adversary has access to
oracles that allow requesting credentials on behalf of honest users, create
signatures by honest users, and open signatures by honest users. In the ideal
world, these three oracles are replaced by simulated counterparts, which produce
outputs independent of the users' secrets. This formulation is given in
\figref{fig:exp-uas-simanon}, where $\Osimanon = (\lbrace\HU,\CU\rbrace\GEN,
\lbrace\II,\OO\rbrace\GEN,\lbrace\II,\OO\rbrace\CORR,\WREG)$.

@@

  \centering
  \procedure[linenumbering]{$\ExpSimAnonb(1^\secpar)$}{%
    \pcif b = 0: \\
    \pcind \parm \gets \Setup(1^\secpar) \\    
    \pcind b^* \gets \adv^{\Osimanon,\OBTAIN,\SIGN,\OPEN}(\parm) \\
    \pcelse: \\
    \pcind (\parm,\NIZKtrap) \gets \SIMSETUP(1^\secpar) \\
    \pcind b^* \gets \adv^{\Osimanon,\SIMOBTAIN,\SIMSIGN,\SIMOPEN}(\parm) \\    
    \pcreturn b^*
  }

  \caption{Simulation-based anonymity experiment for \UAS schemes.}
  \label{fig:exp-uas-anonb}
\end{figure}

\begin{definition}{(Anonymity of \UAS)}
  \label{def:anonymity-uas}  
  We define the advantage \AdvSimAnon of $\adv$ against \ExpSimAnonb as
  $\AdvSimAnon=|\Pr\lbrack\ExpSimAnono(1^\secpar)=1\rbrack-
  \Pr\lbrack\ExpSimAnonz(1^\secpar)=1\rbrack|$.
  %
  An \UAS scheme satisfies simulatable anonymity if there exists simulators
  \SIMSETUP, \SIMOBTAIN, \SIMSIGN and \SIMOPEN such that, for any p.p.t.
  adversary $\adv$, \AdvSimAnon is a negligible function of $1^\secpar$.
\end{definition}

@@

\begin{figure}[htp!]
    \procedure[linenumbering]{$\ExpForgeSign(1^\secpar)$}{%
      \parm \gets \Setup(1^\secpar) \\
      (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval) \gets \adv^{\Oforgesign}(\parm) \\
      \pcif \exists \uid~\st~(\cdot,\cdot,\Sig,\msg,\feval) \in
      \SIG[\uid]: \pcreturn 0 \\
      \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
      \pcreturn 0 \\
      (\yinsp,\iproof) \gets \Open(\PRVOK[\oid],\siid,\Sig,\msg) \\
      \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg,\feval)
      = 0: \pcreturn 1 \\
      (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets \ExtractSign(\oid,\siid,\Sig,
      \msg,\feval) \\
      (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg) \\
      \pcif \yeval \neq \yeval^0: \pcreturn 1 \\
      \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp
      \lor \yinsp \neq \yinsp':
      \pcreturn 1 \\
      \pcif \exists \cred \in \scred~\st~\IdentifyCred(\usk,\attrs_{\cred},\cred) = 0:
      \pcreturn 1 \\
      \pcif \nexists \uid~\st~\IdentifyUK(\uid,\usk) = 1: \pcreturn 1 \\
      \pcreturn 0
    }
  \caption{Experiment for unforgeability of signatures in \UAS schemes.}
  \label{fig:exp-uas-unfor-sign}
\end{figure}

@@

\begin{figure}[htp!]
  \procedure[linenumbering]{$\ExpNonframe(1^\secpar)$ \todo{Updated win conditions here. Update proof.}}{%
    \parm \gets \Setup(1^\secpar) \\
    (\oid,\siid,\Sig=(\sig,\yeval,\ceval),\msg,\feval,\yinsp,\iproof) \gets
    \adv^{\Oframe}(\parm) \\
%    \pcif \exists \uid~\st~(\cdot,\cdot,\sig,\yeval,\msg,\feval) \in \SIG[\uid]:
%    \pcreturn 0 \\
    \pcif \Verify(\PUBOK[\oid],\PUBIK[\siid],\Sig,\msg,\feval) = 0:
    \pcreturn 0 \\
    \pcif \Judge(\PUBOK[\oid],\PUBIK[\siid],\yinsp,\iproof,\Sig,\msg) = 0:
    \pcreturn 0 \\
    (\usk,\scred,\attrs_{\scred},\yinsp',r) \gets
    \ExtractSign(\oid,\siid,\Sig,\msg,\feval) \\
    (\yeval^0,\yeval^1) \gets \feval(\usk,\scred,\msg)~\pccomment{\todo{New}} \\
    \pcif \nexists \uid \in \HU~\st~\UK[\uid] = \usk: \pcreturn 0 \\
    \pcif \nexists (\cdot,\cdot,\Sig,\msg,\feval) \in \SIG[\uid]: \pcreturn 1 \\
    \pcif \finsp((\yeval^0,\yeval^1),\usk,\scred,\msg) \neq \yinsp \lor
    \yinsp \neq \yinsp': \pcreturn 1~\pccomment{\todo{1st or part is new}} \\
    \pcif \yeval \neq \yeval^0: \pcreturn 1~\pccomment{\todo{New}} \\
    \pcreturn 0
  }
  \caption{Experiment for non-frameability on \UAS schemes.}
  \label{fig:exp-uas-frame}
\end{figure}

### 2022-06-03 prism-backend/research/gsac/sec-uas.tex
Upgrading definitions and proofs.

\begin{figure}[ht!]
  \input{figures/proof-blocks-uas.tex}
  \caption{Comparison of statements proved per operation in \GSAC and \UAS.
    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
    encryption of $y$; $D(z)$ means proving correct decryption of $z$. In
    \UAS, solid boxes span configurable statements that control issuance; dashed
    boxes span configurable statements that control utility; dotted boxes span
    configurable statements that control accountability. Unboxed statements are
    fixed, and are thus common to all \GSAC/\UAS schemes.}
  \label{fig:proof-blocks-uas}
\end{figure}

>>>>

\begin{figure}[ht!]
  \input{figures/proof-blocks-uas.tex}
  \caption{Comparison of statements proved per operation in \GSAC and \UAS.
    $K(x)$ means proving knowledge of $x$; $E(y)$ means proving correct
    encryption of $y$; $D(z)$ means proving correct decryption of (an encryption
    of) $z$. In \UAS, solid boxes span configurable statements that control
    issuance; dashed boxes span configurable statements that control utility;
    dotted boxes span configurable statements that control accountability.
    Unboxed statements are fixed, and are thus common to all \GSAC/\UAS
    schemes.\todo{Add a new $\finsp^1$ at opening time, that also relies on
    $\yinsp^1$? Does this enable some use case?}}
  \label{fig:proof-blocks-uas}
\end{figure}

### 2022-06-03 prism-backend/research/gsac/security-uas.tex
Upgrading definitions and proofs.

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
  Moreover, all the credentials employed to honestly produce the signature,
  identified with \scid, meet their respective issuance policies due to
  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
  output of \feval matches \yeval at line $10$, which is furthermore computed
  over $\usk=\UK[\uid]$ due to correctness of the commitment scheme. Finally,
  correctness of the NIZKs for $\NIZKRel_{\Sign}$ and $\NIZKRel_{\Open}$, and
  correctness of the encryption scheme, ensure that \Judge accepts the proof
  produced by \Open, and \yinsp is the correct value for the chosen
  $\finsp^{\oid}$.
\end{proof}

@@

\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

  Finally, consider the definition of $\AdvAnon=|\Pr\lbrack
  \ExpAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$. As
  argued, $G_1$ is indistinguishable from $\ExpAnonb$, thus
  $\AdvAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvAnon is negligible.
  %
  \qed
\end{proof}

>>>>

\begin{proof}[\thmref{thm:correctness-uas}; Correctness of \CUASGen]
  By correctness of \SBCM and the NIZK for $\NIZKRel_{\Sign}$, the signature
  produced at line 5 of \ExpCorrect is accepted at line 6 by \Verify.
  Moreover, all the credentials employed to honestly produce the signature,
  identified with \scid, meet their respective issuance policies due to
  correctness of the NIZK for $\NIZKRel_{\Issue}$, so no $\fissue^\cid$ check
  returns $0$ at line 9. Similarly, as $\feval \in \famfeval$ is checked at
  line 3, and due to correctness of the NIZK for $\NIZKRel_{\Sign}$, the
  output of \feval matches $\yeval^0$ at line $11$, which must have been
  computed over $\usk=\UK[\uid]$, as in line $10$, due to correctness of the
  commitment scheme. Finally, correctness of the NIZKs for $\NIZKRel_{\Sign}$
  and $\NIZKRel_{\Open}$, and correctness of the encryption scheme, ensure that
  \Judge accepts the proof produced by \Open, and \yinsp is the correct value
  for the chosen $\finsp^{\oid}$.
\end{proof}

@@

\begin{proof}[\thmref{thm:anonymity-uas}; Anonymity of \CUASGen]
  First, we define \SimSetup, \SIMOBTAIN, \SIMSIGN and \SIMOPEN as in
  \figref{fig:anon-sim}.

  \begin{figure}[ht!]
  \begin{minipage}[t]{\textwidth}
    \procedure{$\SimSetup(\secpar,\AttrSpace)$}{%
      \textrm{Parse}~\secpar~\textrm{as}~(\cdot,\secpar_{\NIZK},\cdot,\cdot) \\
      (\NIZKcrs_{\Issue},\NIZKtrap_{\Issue})
      \gets \NIZKSimSetup^{\NIZKRel_{\Issue}}(\secpar_{\NIZK}) \\
      (\NIZKcrs_{\Sign},\NIZKtrap_{\Sign})
      \gets \NIZKSimSetup^{\NIZKRel_{\Sign}}(\secpar_{\NIZK}) \\
      (\NIZKcrs_{\Open},\NIZKtrap_{\Open})
      \gets \NIZKSimSetup^{\NIZKRel_{\Open}}(\secpar_{\NIZK}) \\
      \textrm{Compute}~\Cparm,\SBCMparm,\Sparm,\Eparm~\textrm{as in}~\Setup \\
      \pcreturn ((\Cparm,\SBCMparm,\Sparm,\Eparm,\NIZKcrs_{\Issue},
      \NIZKcrs_{\Sign},\NIZKcrs_{\Open},\AttrSpace),
      (\NIZKtrap_{\Issue},\NIZKtrap_{\Sign},\NIZKtrap_{\Open})) \\
    }

    \begin{minipage}[t]{\textwidth}
      \begin{minipage}[t]{0.5\textwidth}
        \procedure{$\SIMOBTAIN(\cid,\uid,\iid,\attrs,\scid)$}{%
          \pcif \uid \notin \HU: \pcreturn \bot \\
          \pcif \iid \notin \CI: \pcreturn \bot \\
          \pcif \CRED[\cid] \neq \bot: \pcreturn \bot \\
          \sipk_{\scred} \gets \PUBIK[\scid] \\
          \langle \cred, \cdot \rangle \gets
          \langle SimObt(\attrs,\PUBIK[\iid],\sipk_{\scred}),\adv \rangle \\
          \CRED[\cid] \gets (\uid, \cred, \iid, \attrs, \scid, \siid) \\
          \pcreturn \top \\      
        }
        \end{minipage}
        \begin{minipage}[t]{0.5\textwidth}
          \procedure{$SimObt(\attrs,\sipk_{\scred})$}{%
            \textrm{Runs \SBCM}
            \textrm{Runs like \Obtain, replacing calls to
            $\NIZKProve^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},
            (\Ccom,\attrs,\sipk_{\scred}),
            (\usk,\scred,\attrs_{\scred},r))$ with calls to
            $\NIZKSim^{\NIZKRel_{\Issue}}(\NIZKcrs_{\Issue},\NIZKtrap_{\Issue},
            (\Ccom,\attrs,\sipk_{\scred}))$}
        }
        \end{minipage}
      \end{minipage}
    \procedure{$\SIMSIGN(\oid,\uid,\scid,\msg,\feval)$}{%
      \pcreturn \SBCMVerify(\ipk_{\cred},\cred,\usk,\attrs_{\cred}) \\
    }

    \procedure{$\SIMOPEN(\oid,\Sig,\msg)$}{%
      \pcreturn 0
    }
  \end{minipage}
  \label{fig:sim-anon}
  \caption{Definition of \SimSetup, \SIMOBTAIN, \SIMSIGN, and \SIMOPEN for
    anonymity in \CUASGen.}
\end{figure}

  \iffalse
  In this proof, we restrict to the case in which the adversary can only make
  one query to the challenge oracle. Note however that the generalization to
  polynomially many queries given in \cite{bsz05} applies here too (with the
  corresponding security loss). Thus, proving security for one query to the
  challenge oracle is enough.

@@

  Finally, consider the definition of $\AdvAnon=|\Pr\lbrack
  \ExpAnono(1^\secpar)=1\rbrack-\Pr\lbrack\ExpAnonz(1^\secpar)=1\rbrack|$. As
  argued, $G_1$ is indistinguishable from $\ExpAnonb$, thus
  $\AdvAnon \approx |\Pr\lbrack G_1^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_1^0(1^\secpar)=1\rbrack| \approx
  |\Pr\lbrack G_2^1(1^\secpar)=1\rbrack-\Pr\lbrack
  G_2^0(1^\secpar)=1\rbrack|$. Since $G_2^1=G_2^0$, it follows that
  \AdvAnon is negligible.
  \fi
  %
  \qed
\end{proof}
